\documentclass[9pt,a4paper]{extarticle}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[top=0.4in, bottom=0.35in, left=0.5in, right=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{xcolor}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\renewcommand{\arraystretch}{1.15}

% Section titles as per guide
\titleformat{\section}{\small\bfseries\uppercase}{}{0em}{}[\vspace{-2pt}\rule{\textwidth}{0.6pt}\vspace{-4pt}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

% Compact list spacing
\setlist[itemize]{leftmargin=12pt, label={--}, nosep, before=\vspace{2pt}, after=\vspace{2pt}}

\begin{document}

\begin{center}
{\Large\bfseries PRASHANT KUMAR}\\[3pt]
{\footnotesize +91 8477993577 \quad\textbar\quad \href{mailto:prashantkumar_24ci01@dtu.ac.in}{prashantkumar\_24ci01@dtu.ac.in} \quad\textbar\quad \href{https://www.linkedin.com/in/prashant-kumar-3551b6214} \quad	extbar\quad \href{https://github.com/prashantkumar24ci01-blip}{github.com/prashantkumar24ci01-blip}{linkedin.com/in/prashant-kumar-3551b6214} \quad	extbar\quad \href{https://github.com/prashantkumar24ci01-blip}{github.com/prashantkumar24ci01-blip}}\\[3pt]
{\footnotesize M.Tech (Control \& Instrumentation) --- Delhi Technological University \quad\textbar\quad GATE 2024 Qualified (EE)}\\[1pt]
{\footnotesize\color{gray}AI Catalyst Intern --- Havells CRI}
\end{center}
\vspace{2pt}

\section{Education}

\begin{tabular}{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{6.8cm}>{\raggedright\arraybackslash}p{1.5cm}}
\textbf{Degree} & \textbf{Year} & \textbf{Institution} & \textbf{CGPA/\%} \\
M.Tech (C\&I) & 2024--26 & Delhi Technological University & 74.5\% \\
B.Tech (EE) & 2017--21 & MJP Rohilkhand University, Bareilly & 69.2\% \\
\end{tabular}

\section{Technical Skills}

\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}p{\dimexpr\textwidth-2.8cm-4\tabcolsep\relax}}
\textbf{AI \& ML Stack} & RAG Pipelines, ChromaDB (Vector DB), Sentence Transformers, LLM Orchestration, NLP (Embeddings, Semantic Search), OpenRouter API, Model Evaluation \\
\textbf{Programming} & Python (NumPy, Pandas, Matplotlib, HuggingFace), MATLAB, Shell/Bash, Git \\
\textbf{Engineering Tools} & SPICE Simulation (ngspice, PSpice), Cadence Virtuoso, OrCAD, MATLAB/Simulink, Testbench Automation \\
\textbf{Core Competencies} & Workflow Analysis \& Automation, Engineering Productivity, Design-of-Experiments, Signal Processing, Control Systems, Circuit Analysis \\
\textbf{Platforms} & Linux (Redhat, Debian, NixOS), Windows, WSL \\
\end{tabular}

\section{Projects}

\noindent\textbf{AnalogCheck --- AI-Powered SPICE Error Checker with RAG Pipeline} \hfill\textbf{Capstone Project}\\
\emph{Python, ChromaDB, Sentence Transformers, OpenRouter LLM, ngspice}
\begin{itemize}
  \item Built CLI tool that semantically checks SPICE netlists for common IC design errors, combining 5 deterministic health checks with an AI reasoning layer --- directly analogous to engineering copilot deployment.
  \item Implemented RAG pipeline: 20 annotated IC error patterns + PSpice reference documents embedded via \texttt{all-MiniLM-L6-v2} into ChromaDB vector store.
  \item Integrated LLM reasoning (OpenRouter API) for error explanation and fix suggestion generation --- demonstrates LLM orchestration, prompt engineering, and AI tool calling.
  \item Automated ngspice subprocess validation: parses simulation output, detects DC convergence failures, floating nodes, and missing ground --- AI-driven engineering workflow automation.
  \item Generated structured JSON/Markdown reports; designed for CI/CD integration into design verification flows.
\end{itemize}
\vspace{6pt}

\noindent\textbf{Engineering Workflow Automation: Bias-Sweep Testbench Generator}\\
\emph{Python, ngspice, MATLAB}
\begin{itemize}
  \item Developed automated AC analysis testbench generator that sweeps 4 transistor bias conditions and extracts gain, phase margin, and $-3$\ dB bandwidth --- replaced manual per-condition testbench editing.
  \item Demonstrated 5$\times$ reduction in simulation setup time; generated comparative performance reports programmatically.
\end{itemize}
\vspace{6pt}

\noindent\textbf{M.Tech Thesis: Transistor-Level Analog Filter Verification}\\
\emph{ngspice, Python, MATLAB, 0.18\ $\mu$m CMOS BSIM3v3}
\begin{itemize}
  \item Verified single-OTRA biquad filter at three abstraction tiers (symbolic, behavioral, transistor-level) --- systematic multi-level validation methodology transferable to AI model evaluation frameworks.
  \item Identified and resolved high-pass passband droop via systematic DOE bias sweep across 4 operating points --- data-driven root-cause analysis.
\end{itemize}

\section{Additional Experience}

\noindent\textbf{Teaching Assistant} --- Dept. of Electrical Engineering, DTU \hfill\textbf{Aug 2024 -- Present}
\begin{itemize}
  \item Conducted VLSI and digital logic labs for 30+ students; developed automated testbenches for functional verification.
\end{itemize}

\section{Achievements}
\begin{itemize}
  \item GATE 2024 Qualified (Electrical Engineering) --- top 15\% nationally.
  \item Published IEEE Conference Paper: ``Application \& Performance Comparison of Electrical Motors in HEVs.''
  \item Built and deployed 2 AI/ML tools (AnalogCheck RAG pipeline + automated testbench generator) demonstrating end-to-end AI project execution --- from problem identification to production-ready output.
\end{itemize}

\end{document}